### 2019-12-27 paper/birth_spacing_lit.tex

The empirical results based on the ﬁrst hypothesis show that the level
of industrialization of the local economy does not have a differential
effect on birth spacing across educational groups. However, empirical
results using measures of the availability of a family planning program
show a differential effect on delaying births across educational groups.

@@

My ﬁndings are consistent with the hypothesis that more educated women
are better at adopting new contraceptive technology.

>>>>

The empirical results based on the first hypothesis show that the level
of industrialization of the local economy does not have a differential
effect on birth spacing across educational groups. However, empirical
results using measures of the availability of a family planning program
show a differential effect on delaying births across educational groups.

@@

My findings are consistent with the hypothesis that more educated women
are better at adopting new contraceptive technology.

### 2019-12-27 paper/conceptual_framework.tex

This section provides a conceptual framework for understanding what determines  
birth spacing.
I first discuss the main determinants of spacing examined in the prior research, and 
then turn to how son preference and sex selection fits into the decisions on spacing.
Since sex selection and education are closely linked, I pay special attention to how 
education affects spacing.

In the simplest possible dynamic model of fertility, the spacing decision is trivial.
Assume that parents derive benefits from the presence of children, rather than from 
the births themselves, that spacing of children by itself does impact the parental utility, 
and that the parents perfectly control when to have children. 
The optimal decision is then to have the children as early as possible 
\citep{Newman1988}.
The simplest model does not fit the observed spacing patterns, which suggests 
that one or more of the assumptions are wrong.

@@

Despite a general belief that better access to and knowledge of contraception 
should lead to longer average spacing, the empirical relationship between contraception 
use and birth spacing is ambiguous 
\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
This lack of evidence is consistent with the ambiguous theoretical effect of introducing 
modern contraceptives on birth spacing.
On the one hand, in the absence of high-efficacy contraceptive technologies, parents may try to 
avoid overshooting their desired number of children by spacing their children further apart
than they would otherwise do.
Increased reliability of the access to and effectiveness of contraceptives then lead to 
shorter birth intervals because parents are more confident they can effectively
stop childbearing when they want \citep{Keyfitz1971,Heckman1976}.
On the other hand, when contraceptives are ineffective, some birth intervals will
be shorter than ideal, in the way discussed below, through simple random variation.
With increased reliability of contraceptive efforts, parents can better avoid too short 
birth spacing, and average spacing should go up.

@@

Third, parents incur both direct and time costs when they have children, 
and economic factors can, therefore, affect birth spacing \citep{Hotz1997,Schultz1997}.
I divide the economic factors into the effects of price and income shocks,
the expected income trajectory of the husband and wife,
and economies of scale considerations.

@@

In the absence of perfect capital markets, theory predicts that the steeper 
the parents' lifetime income profile, the longer the spacing between births, 
which suggests that with economic development we should see a general increase 
in spacing across education groups and that this increase in spacing should be 
stronger with increasing education levels
\citep{Heckman1976,Wolpin1984,Newman1988}.
The idea is that although parents would prefer to have their children as early 
as possible to enjoy them for longer, there is also a direct cost to children.
Early on income is low, which means that the marginal utility of consumption is 
higher, making parents less willing to give up consumption now to have a child, 
compare to later when they know that their income will be higher 
\citep{Newman1984,Happel1984}.

The income profile argument assumes that parents know their future income, 
but income and price shocks may also affect spacing. 
A temporary, higher cost of women's time or a lower household income, will 
temporarily decrease fertility and, thereby, increase birth spacing 
\citep{Moffitt1984,Hotz1988,Portner2001,Alam2018}.
Increasing education likely reduces the risk of income shocks, but the 
effect on other types of shocks that might impact the spacing is unclear.

@@

It is not, however, immediately apparent that we should expect shorter spacing in 
the absence of boys, if short spacing lowers the survival probability of the 
next child, as discussed above.
There are two potential reasons why parents might still try to conceive sooner 
in the absence of boys.%
\footnote{
The significant differences in spacing by sex composition indicate that
parents control the timing of birth, at least to some extent.
In Matlab, the effect of son preference on birth spacing is stronger in 
areas with better access to family planning \citep{Rahman1993}.
}
One possibility is that parents do not realize that short spacing is potentially
detrimental to the next child's health, resulting in high mortality for both boys 
and girls born after short spacing across all households whether or not they have 
a son preference.%
\footnote{
We may even see a higher likelihood of dying for sons than girls, given that boys 
have naturally higher mortality.
}

The other possibility is that parents realize that short spacing has adverse 
health effects, but their son-preference is so strong that they are willing to 
divert substantial resources to the next child if it is a boy.
Assuming that these investments can compensate for the adverse effects,
we should see significant differences in mortality across sex for short-spacing 
children in the absence of boys.
If a son is born, his mortality risk should be substantially lower than expected 
for the spacing duration, and we should expect worse outcomes for the other 
children (all girls).
If a girl is born, there are two possible outcomes.
If parents treat all children/girls the same, we should see a slight worsening in 
health outcomes because fewer resources are available per child; 
if they do not, the last girl will have a much lower likelihood of surviving 
because the parents' incentive is to invest in their prior children rather than 
the new child.

As mentioned above, the adverse effects of shorter spacing are strongly mitigated 
by higher education, which, in theory, allows better-educated women to have shorter
spacing in the absence of a boy without substantial increasing mortality risk.
Differences in mortality outcomes across boys and girls are still possible,
but should not be as large as for less-educated women.

With the introduction of sex selection, parents can avoid the birth of girls, 
although at the cost of the procedure and having to wait longer until 
the next child if they abort the fetus.
The question is, who is likely to use sex selection, when, and why?

Theory suggests that the lower the desired fertility, the 
higher the likelihood of sex selection \citep{Portner2015b}.
Simple probabilities drive this prediction:
in the absence of sex selection, 
48.8 percent will not have a son when only having one child, 
23.8 percent for two children, 11.6 percent for three children, 
5.7 percent for four children, 2.8 percent for five children, 
and 1.4 percent for six children.
Furthermore, for a given level of desired fertility, the higher
the parity, the higher is the likelihood of using sex selection.

The higher the cost of prenatal sex determination and abortion,
the less use we should see.
Similarly, any potential adverse effects on the mother and offspring 
from repeated abortions would also tend to reduce the use of sex 
selection---provided that parents are aware of these costs.
Finally, the more abortions between births, the less the opportunity 
there is to take advantage of any economies of scale in childrearing.

The use of sex selection in India increases with education and is higher 
in urban areas than in rural
\citep{das_gupta97,retherford03b,jha06,Guilmoto2009a,Bongaarts2013,Portner2015b,
Jayachandran2017}.
Women with more education generally have lower desired fertility, either 
because of the higher opportunity cost of time or because of other changes 
in the preferred number of children.%
\footnote{
It is also possible that the effect is driven by a stronger son preference, although 
higher education women have shown declining stated son preference \citep{bhat03,pande07}.
}
Better-educated women also tend to live in households with higher 
income, which better enables them to access prenatal sex determination 
and lowers the relative costs of using sex selection.

@@

In summary, birth spacing is affected by female education through 
multiple pathways, with the main one of interest here the use of 
sex selection. 
But, to fully understand how sex selection affects spacing, we also 
need to understand the other changes that affect birth spacing over time.
The most likely factors are the changes in household income and 
wealth and the improvements in health as India has developed.
I, therefore, now look at how female education and labor force 
participation has changed over time in India.

>>>>

This section provides a conceptual framework for understanding what determines  
birth spacing.
I first discuss the main determinants of spacing examined in the prior research, and 
then how son preference and sex selection fits into the spacing decisions.
Since sex selection and education are closely linked, I pay special attention to how 
education affects spacing.

In the simplest possible dynamic model of fertility, the spacing decision is trivial.
Assume that parents derive benefits from the presence of children, not their births, 
that spacing of children does impact parents' utility, 
and that the parents fully control when to have children. 
The optimal decision then is to have the children as early as possible 
\citep{Newman1988}.
The simplest model does not fit the observed spacing patterns, which suggests 
that one or more of the assumptions are wrong.

@@

Despite a general belief that better access to and knowledge of contraception 
should lengthen average spacing, the empirical relationship between contraception 
use and birth spacing is ambiguous 
\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
This lack of evidence is consistent with the ambiguous theoretical effect of introducing 
modern contraceptives on birth spacing.
On the one hand, in the absence of high-efficacy contraceptive technologies, parents may 
try to avoid overshooting their desired number of children by spacing their children 
further apart than they would otherwise do.
Increased reliability of the access to and effectiveness of contraceptives then lead to 
shorter birth intervals because parents are more confident they can effectively
stop childbearing when they want \citep{Keyfitz1971,Heckman1976}.
On the other hand, through simple random variation, when contraceptives are ineffective, 
some birth intervals will be shorter than ideal, in the way discussed below.
With increased reliability of contraceptive efforts, parents can better avoid too short 
birth spacing, and average spacing should go up.

@@

Third, parents incur both direct and time costs when they have children, 
and economic considerations can, therefore, affect birth spacing 
\citep{Hotz1997,Schultz1997}.
I divide the economic factors into the effects of economies of scale and
the expected income trajectory of the husband and wife.

@@

In the absence of perfect capital markets, theory predicts that the steeper 
the parents' lifetime income profile, the longer the spacing between births, 
which suggests that with economic development we should see a general increase 
in spacing across education groups and that this increase in spacing should be 
stronger with increasing education levels
\citep{Heckman1976,Wolpin1984,Newman1988}.
The idea is that although parents would prefer to have their children as early 
as possible to enjoy them for longer, there is also a direct cost to children.
Income is low early on, which means that the marginal utility of consumption is 
higher, making parents less willing to give up consumption to have a child, 
compare to later when they know that their income will be higher 
\citep{Newman1984,Happel1984}.

@@

If short spacing lowers the survival probability of the next child, as discussed above,
it is not, however, apparent that we should expect shorter spacing in the absence of boys.
There are two potential reasons why parents might still try to conceive sooner 
in the absence of boys.%
\footnote{
The significant differences in spacing by sex composition indicate that
parents control the timing of birth, at least to some extent.
In Matlab, the effect of son preference on birth spacing is stronger in 
areas with better access to family planning \citep{Rahman1993}.
}
One possibility is that parents do not realize that short spacing is potentially
detrimental to the next child's health, resulting in high mortality for both boys 
and girls born after short spacing across all households.

The other possibility is that parents realize that short spacing has adverse 
health effects, but their preference for sons is so strong that they are willing to 
divert substantial resources to the next child if it is a boy.
Assuming that these investments can compensate for the adverse effects,
we should see significant differences in mortality across sex for short-spacing 
children in the absence of boys.
If a son is born, his mortality risk should be substantially lower than expected 
for the spacing duration, and we should expect worse outcomes for the other 
children (all girls).
If a girl is born, there are two possible outcomes.
If parents treat all children/girls the same, we should see a slight worsening in 
health outcomes because fewer resources are available per child; 
if they do not, the last girl will have a much lower likelihood of surviving 
because the parents' incentive is to invest in their prior children rather than 
the new child.

With the adverse effects of shorter spacing strongly mitigated by higher education,
better-educated women can, in theory, have shorter spacing in the absence of a boy 
without substantial increasing mortality risk.
Differences in mortality outcomes across boys and girls are still possible,
but should not be as large as for less-educated women.

With the introduction of sex selection, parents can avoid the birth of girls, 
although at the cost of the procedure and having to wait longer until 
the next child if they abort the fetus.

Theory suggests that sex selection increases with lower desired fertility, and, for a 
given desired number of children, the higher the parity \citep{Portner2015b}.
The increased use of sex selection in India with education and in urban
areas is consistent with a lower desired fertility for both groups,
either because of the higher cost of children or because of other
changes in the preferred number of children
\citep{das_gupta97,retherford03b,jha06,Guilmoto2009a,Bongaarts2013,Portner2015b,
Jayachandran2017}.%
\footnote{
Stronger son preference could also contribute, but better-educated women 
have declining stated son preference over time \citep{bhat03,pande07}.
}

The higher the cost of prenatal sex determination and abortion, the less use we should 
see.
Similarly, any potential adverse effects on the mother and offspring 
from repeated abortions should also reduce the use of sex selection---provided that 
parents are aware of these costs.
Furthermore, the more abortions between births, the less the parents can take advantage 
of economies of scale.
Better-educated women tend to live in households with higher income, which better enables 
them to access prenatal sex determination and lowers the relative costs of using sex 
selection.

@@

In summary, birth spacing is affected by female education through 
multiple pathways, with the main one of interest here the use of 
sex selection. 
But, to fully understand how sex selection affects spacing, we also 
need to understand the other changes that affect birth spacing over time.
The most likely factors are the changes in household income and 
wealth and the improvements in health as India has developed.
I, therefore, examine how female education and labor force 
participation has changed over time in India.

### 2019-12-27 paper/sex_selection_spacing-ver3.tex

Third, parents incur both direct and time costs when they have children, 
and economic considerations can, therefore, affect birth spacing 
\citep{Hotz1997,Schultz1997}.
I divide the economic factors into the effects of economies of scale and
the expected income trajectory of the husband and wife.

The expected effect of economies of scale in childrearing, which, for example, 
can arise because taking care of two young children does not take twice as much 
time as taking care of one child, is to shorten intervals between births
\citep{Vijverberg1982,Espenshade1984}.
To the extent that children require the mother to do less market work, parents 
can lower the cost of children by reducing birth spacing.
In this case, better-educated women will both have lower fertility and shorter
spacing than less-educated women because of their higher opportunity cost of time 
\citep{Ross1974,Newman1981,Newman1984}.
However, if the mother mainly works at home or as household income increases, there 
is less incentive to space children for this reason.

In the absence of perfect capital markets, theory predicts that the steeper 
the parents' lifetime income profile, the longer the spacing between births, 
which suggests that with economic development we should see a general increase 
in spacing across education groups and that this increase in spacing should be 
stronger with increasing education levels
\citep{Heckman1976,Wolpin1984,Newman1988}.
The idea is that although parents would prefer to have their children as early 
as possible to enjoy them for longer, there is also a direct cost to children.
Income is low early on, which means that the marginal utility of consumption is 
higher, making parents less willing to give up consumption to have a child, 
compare to later when they know that their income will be higher 
\citep{Newman1984,Happel1984}.

@@

@@

>>>>

Third, parents incur both direct and time costs when they have children, 
and economic considerations can, therefore, affect birth spacing 
\citep{Hotz1997,schultz97}.
I divide the economic factors into the effects of economies of scale and
the expected income trajectory of the husband and wife.

The expected effect of economies of scale in childrearing, which, for example, 
can arise because taking care of two young children does not take twice as much 
time as taking care of one child, is to shorten intervals between births
\citep{Vijverberg1982}.
To the extent that children require the mother to do less market work, parents 
can lower the cost of children by reducing birth spacing.
In this case, better-educated women will both have lower fertility and shorter
spacing than less-educated women because of their higher opportunity cost of time 
\citep{Ross1974,Newman1984}.
However, if the mother mainly works at home or as household income increases, there 
is less incentive to space children for this reason.

In the absence of perfect capital markets, theory predicts that the steeper 
the parents' lifetime income profile, the longer the spacing between births, 
which suggests that with economic development we should see a general increase 
in spacing across education groups and that this increase in spacing should be 
stronger with increasing education levels
\citep{Heckman1976,wolpin84,Newman1988}.
The idea is that although parents would prefer to have their children as early 
as possible to enjoy them for longer, there is also a direct cost to children.
Income is low early on, which means that the marginal utility of consumption is 
higher, making parents less willing to give up consumption to have a child, 
compare to later when they know that their income will be higher 
\citep{Newman1984,Happel1984}.

@@

\section{Female Education and Labor Force Participation in India}

Female educational attainment has increased substantially over time.
Figure \ref{fig:education_over_time} shows the distribution of schooling by birth 
cohort for urban and rural women, 
twenty years or older, whether married or not, based on the four rounds of the NFHS.
The education groups are no education, one to seven years, and eight to eleven years,
and twelve years and above.

\begin{figure}[htpb]
\centering
\subfloat[Rural]{
    \begin{minipage}{0.49\textwidth}
        \includegraphics[width=\textwidth]{educ_over_time_rural}
    \end{minipage}
} 
\subfloat[Urban]{
    \begin{minipage}{0.49\textwidth}
        \includegraphics[width=\textwidth]{educ_over_time_urban} 
    \end{minipage}
}
\caption{Distribution of education by cohort for women twenty years or older at survey}
\label{fig:education_over_time}
\end{figure}

For rural areas, the percentage of women with no education has gone from around 90 percent
for the 1930s cohorts to less than 20 percent for the 1990s cohorts. 
The proportion of women with one to seven years of education has remained remarkably
constant at around ten percent.
The difference is made up by the women with eight or more years of education, who have
gone from almost zero for the 1930 cohort to more than sixty percent for the 1990s cohorts,
with about half in the eight to eleven years group and 
the other half in the twelve years or more group.

Female education is higher in urban areas than in rural areas.
Around sixty percent of urban women born in the 1930s had no education, 25 percent had
between one and seven years, about 10 had eight or more years of education, and only
five percent has twelve years or more.
The proportions with no education and one to seven years have both declined to just below 
ten percent for the latest cohort.
Although the proportion of women with eight to eleven years of education has increased
to about twenty, most of the increase in urban female education has come from the 
twelve plus group, which now account for more than half of all urban women.

Even as the level of female education has increased, the female labor force participation 
in both urban and rural areas has stagnated or decreased
\citep{Klasen2015,Afridi2018,Bhargava2018,Chatterjee2018, Bhargava2019}.
A decline in female labor force participation at the beginning of development is
consistent with the hypothesis of a U-shaped labor force participation as a country
develops \citep{Goldin1994}.
India's female labor force participation is, however, lower than most other
countries and more in line with countries in the Middle East and North Africa, and
does not yet show any signs of increasing
\citep{Klasen2015,Chatterjee2018}.

Theory predicts that increasing women's wages leads to higher labor force participation, 
while both a higher male income and stronger social restrictions on working, possibly in 
specific industries or jobs, reduce female labor supply \citep{Goldin1994}.
India's economy has grown substantially since the mid-seventies, with
an average annual growth rate of about 5.5 percent from 1978 to 2004 \citet{Bosworth2008}.
As a result, real wages for both men and women have almost doubled between 1987 and 2011 
\citep{Klasen2015}.
Despite the increases in wages and the higher female education, the mean male wage is
still close to 70 percent higher than the mean female wage \citep{Bhargava2018}.
Furthermore, the development in women's wages is not uniform across education 
levels \citep{Klasen2015,Bhargava2018}.
The real wages for women with middle school education or below have converged. 
For women with secondary education, the change over time depends on the sample used,
with some showing a substantial decline and others a modest increase.
Women with more than secondary education experienced an increased in their real 
wages, especially in cities.

After controlling for household characteristics and husband income, there is
still a U-shaped relationship between female education and labor supply with the
lowest labor force participation for women with secondary education \citep{Chatterjee2018}.
There are two possible explanations for this effect, both directly related to the strong
pro-male bias in India.
First, it becomes less socially acceptable for women to work in manual labor as their
education increases, and women are still mostly excluded from white-collar
employment despite robust economic growth \citep{Klasen2015,Chatterjee2018}.
Second, with increasing education, women's productivity at home also increases, especially
in the production of offspring human capital.
With relatively more boys born because of increased access to sex-selective 
abortions and an increasing male income, demand for better-educated women can 
increase, even if they do not participate in the labor market \citep{Behrman1999}.

Figure \ref{fig:work_by_survey} shows the percent of married women who are 
currently working at the time of the survey by age group and education level.
No other labor force participation question is consistently available across all 
four surveys. 
Because the question refers to currently working, the percentages will be lower 
than what other studies have found. 
Furthermore, since the question is asked only of married women, the overall female labor 
force participation might have developed differently, especially since many young, 
unmarried women have begun working in, for example, the business process 
outsourcing industry, which, in turn, has increased girls' schooling investments
\citep{Jensen2012}.

\begin{figure}[!htpb]
\centering
\rotatebox[origin=c]{90}{\small{40 Years or Older}}
\subfloat[Rural]{
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=\textwidth]{currently_working_rural_40}
    \end{minipage}
} 
\subfloat[Urban]{
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=\textwidth]{currently_working_urban_40} 
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{30 to 39 Years Old}}
\subfloat[Rural]{
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=\textwidth]{currently_working_rural_30}
    \end{minipage}
} 
\subfloat[Urban]{
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=\textwidth]{currently_working_urban_30} 
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{20 to 29 Years Old}}
\subfloat[Rural]{
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=\textwidth]{currently_working_rural_20}
    \end{minipage}
} 
\subfloat[Urban]{
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=\textwidth]{currently_working_urban_20} 
    \end{minipage}
}
\caption{Percentage of married women who were working at the time of the 
survey by age group and area of residence}
\label{fig:work_by_survey}
\end{figure}

The U-shaped relationship between education and working holds in most cases with 
the highest percent working for women with either no education or with twelve or 
more years and the lowest for women with eight to eleven years of education.
Women are more likely to report working if they live in rural than urban areas 
and the older they are.
Comparing 1992 and 2015, the percent of women who currently work has either 
remained roughly the same or decreased.
The cases were the numbers were higher in 1999 and 2006 than in 1992 or 2015 
are mostly based on small samples, such as rural women with twelve or more 
years of education in rural areas.

Almost all of the urban women who work receive either cash or a combination of 
cash and in-kind for their work (see Appendix Figure \ref{fig:work_cash_by_survey}). 
Rural women have become more likely to receive cash for their labor over time, 
and the better educated, the more likely they are to receive cash.

Despite this, women across all groups have become substantially more likely to 
work for a family member rather than for themselves or somebody else
(see Appendix Figure \ref{fig:work_family_by_survey}).
Hence, the lower likelihood of working stems mostly from women retracting from 
the general labor market and self-employment.

The increases in female educational attainment imply that access to education 
has expanded beyond the higher castes. 
However, ``Sanskritization'' implies that as lower castes females gain access to 
education and their husbands' income increases, the women adopt higher caste 
norms such as stronger son preference and a retraction from the formal labor 
market \citep{Srinivas1956,Chen1995,Abraham2013,Chatterjee2018}. 
``Sanskritization'' may also lead to an increased aversion to daughters, rather 
than just an increased preference for sons, which, in turn, lowers desired 
fertility \citep{Borooah2004}.

Hence, with substantial increases in husband income and a declining female labor force 
participation, I expect a push toward longer birth spacing over time, independent
of education levels, based on the income effects and the effects of spacing
on child outcomes in the theories above.
The declining percentage of women working suggests that the opportunity cost
effects with increasing education will not be strong enough to shorten the
birth spacing.

As desired fertility decreases with increasing education, I, furthermore, expect 
birth spacing to increase the most among the best-educated because of their 
use of sex selection and because of "Sanskritization" the changing composition 
of women in the better-educated group does not substantially change this 
group's use of sex selection.
Working in the opposite direction is that women with more education can space
their children closer together without substantially increasing child mortality risk.

@@

\section{Characteristics of Women Work Experiences}

\begin{figure}[!htpb]
\centering
\rotatebox[origin=c]{90}{\small{40 Years or Older}}
\subfloat[Rural]{
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=\textwidth]{work_cash_rural_40}
    \end{minipage}
} 
\subfloat[Urban]{
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=\textwidth]{work_cash_urban_40} 
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{30 to 39 Years Old}}
\subfloat[Rural]{
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=\textwidth]{work_cash_rural_30}
    \end{minipage}
} 
\subfloat[Urban]{
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=\textwidth]{work_cash_urban_30} 
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{20 to 29 Years Old}}
\subfloat[Rural]{
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=\textwidth]{work_cash_rural_20}
    \end{minipage}
} 
\subfloat[Urban]{
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=\textwidth]{work_cash_urban_20} 
    \end{minipage}
}
\caption{Percentage of women paid cash or cash and in-kind of those women who were 
working at the time of the survey by age group and area of residence}
\label{fig:work_cash_by_survey}
\end{figure}

\begin{figure}[!htpb]
\centering
\rotatebox[origin=c]{90}{\small{40 Years or Older}}
\subfloat[Rural]{
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=\textwidth]{work_family_rural_40}
    \end{minipage}
} 
\subfloat[Urban]{
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=\textwidth]{work_family_urban_40} 
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{30 to 39 Years Old}}
\subfloat[Rural]{
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=\textwidth]{work_family_rural_30}
    \end{minipage}
} 
\subfloat[Urban]{
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=\textwidth]{work_family_urban_30} 
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{20 to 29 Years Old}}
\subfloat[Rural]{
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=\textwidth]{work_family_rural_20}
    \end{minipage}
} 
\subfloat[Urban]{
    \begin{minipage}{0.45\textwidth}
        \includegraphics[width=\textwidth]{work_family_urban_20} 
    \end{minipage}
}
\caption{Percentage of women who were working for a family of those women who were
working at the time of the survey by age group and area of residence}
\label{fig:work_family_by_survey}
\end{figure}
